---
title: "Tips"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Use of `verbose`

When the argument `verbose = TRUE` is passed to a function, a number of 
information is displayed in the console, including the URL used to call the API.

```{r verbose}
library(ineapir)

# Variables used in the operation IPC and verbose = TRUE
variables <- get_metadata_variables(operation = "IPC", verbose = TRUE)
```

## Use of `validate`
If it is not necessary to validate the values of the arguments passed to a
function, this validation can be turned off with `validate = FALSE`.

```{r validate_1}
# Variables used in the operation IPC with verbose = TRUE and validate = FALSE
variables <- get_metadata_variables(operation = "IPC", verbose = TRUE,
                                    validate = TRUE)
```

This is useful when we are filtering data and the filter we are using is
the one we want. Turning off validation means making fewer API calls

```{r validate_2}
# The filter 
filter <- list("115" = "2",     # variable id = 115, value id = 2
               "3" = "74" ,     # variable id = 3, value id = 74
               "762" = "304092" # variable id = 762, value id = 304092
               )

# Request data using the filter with verbose = TRUE and validate = TRUE
ipc <- get_data_series_filter(operation = "IPC", filter = filter, period = 1,
                       verbose = TRUE)

# Request data using the filter with verbose = TRUE and validate = FALSE
ipc <- get_data_series_filter(operation = "IPC", filter = filter, period = 1,
                       verbose = TRUE, validate = FALSE)
```

## Use of `lang`
It is possible to retrieve information in English passing the argument
`lang = "EN"` to certain functions.

```{r lang_1}
# Variables used in the operation IPC and lang = "EN"
variables <- get_metadata_variables(operation = "IPC", lang = "EN")
variables
```


We can use the English language as well filtering data using shortcuts.

```{r lang_2}
# Filter with the cpi wrapper
filter <- list(cpi = c("annual change" , "overall index"))

# Request data using the filter with shortcut = TRUE and lang = "EN"
cpi <- get_data_table(idTable = 50902, shortcut = TRUE, filter = filter,
                      unnest = TRUE, tip = "A", nlast = 5, lang = "EN")

cpi[,c("Nombre", "T3_Periodo", "Anyo", "Valor")]
```

## Use of `unnest`
When we request data from tables or series using the functions
`get_data_table()`, `get_data_series()` and `get_data_series_filter`, the
`$Data` column containing the data values is a list of data frames, one for each
 entry.

```{r unnest_1}
# Filter with the ipc wrapper
filter <- list(ipc = c("variación anual" , "variación mensual", "índice general"))

# Request data using the filter and unnest = FALSE
ipc <- get_data_table(idTable = 50902, shortcut = TRUE, filter = filter,
                      tip = "A", nlast = 3)

# We have two entries
 ipc[,c("COD","Nombre")]
 
# Data column is a list of two data frames. One for each entry. 
 ipc$Data
```

If we want to get only one data frame for all data values, we can pass
the argument `unnest = TRUE`.

```{r unnest_2}
# Filter with the ipc wrapper
filter <- list(ipc = c("variación anual" , "variación mensual", "índice general"))

# Request data using the filter and unnest = TRUE
ipc <- get_data_table(idTable = 50902, shortcut = TRUE, filter = filter,
                      tip = "A", nlast = 3, unnest = TRUE)

# Unique data frame with 6 rows
ipc[,c("Nombre", "T3_Periodo", "Anyo", "Valor")]
```

## Use of `geocode`
When we request data from Autonomous Communities, provinces or municipalities,
we can get the corresponding INE code of each one by passing the argument
`geocode=TRUE`. Including metadata with `tip="M"` is required for it to work.

```{r geocode}
# Filter with the ipc wrapper
filter <- list(ipc = c("índice$" , "índice general"), prov = "")

# Request data using the filter with geocode = TRUE and tip = "AM"
ipc <- get_data_table(idTable = 50918, shortcut = TRUE, filter = filter,
                      tip = "AM", nlast = 1, unnest = TRUE, geocode = TRUE)

# The Codigo column contains the INE code of the different provinces
ipc[1:5,c("Codigo","Nombre", "T3_Periodo", "Anyo", "Valor")]
```


## Filtering with regular expresions
When we use shortcuts names in the filter, we can also include as values
regular expressions if this helps us filter the data better.

```{r regexp_1}
# Filter with a regular expression for ages between 20 and 25 years old
filter <- list(sexo = "total", edad = "2[0-5]+")

# Request data using the filter with a regular expression
pob <- get_data_table(idTable = 56934, shortcut = TRUE, filter = filter,
                      tip = "A", nlast = 1, unnest = TRUE)

# Only ages between 20 and 25 years old
pob[,c("Nombre", "Anyo", "Valor")]
```


