---
title: "Tips"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Use of `verbose`

When the argument `verbose = TRUE` is passed to a function, a number of 
information is displayed in the console, including the URL used to call the API.

```{r verbose}
library(ineapir)

# Variables used in the operation IPC and verbose = TRUE
variables <- get_metadata_variables(operation = "IPC", verbose = TRUE)
```

## Use of `validate`
If it is not necessary to validate the values of the arguments passed to a
function, this validation can be turned off with `validate = FALSE`.

```{r validate_1}
# Variables used in the operation IPC with verbose = TRUE and validate = FALSE
variables <- get_metadata_variables(operation = "IPC", verbose = TRUE,
                                    validate = TRUE)
```

This is useful when we are filtering data and the filter we are using is
the one we want. Turning off validation means making fewer API calls

```{r validate_2}
# The filter 
filter <- list("115" = "2",     # variable id = 115, value id = 2
               "3" = "74" ,     # variable id = 3, value id = 74
               "762" = "304092" # variable id = 762, value id = 304092
               )

# Request data using the filter with verbose = TRUE and validate = TRUE
ipc <- get_data_series_filter(operation = "IPC", filter = filter, period = 1,
                       verbose = TRUE)

# Request data using the filter with verbose = TRUE and validate = FALSE
ipc <- get_data_series_filter(operation = "IPC", filter = filter, period = 1,
                       verbose = TRUE, validate = FALSE)
```

## Use of `lang`
It is possible to retrieve information in English passing the argument
`lang = "EN"` to certain functions.

```{r lang_1}
# Variables used in the operation IPC and lang = "EN"
variables <- get_metadata_variables(operation = "IPC", lang = "EN")
variables
```


We can use the English language as well filtering data using shortcuts.

```{r tabla_filter_2}
# Filter with the ipc wrapper
filter <- list(cpi = c("annual change" , "overall index"))

# Request data using the filter with shortcut = TRUE and lang = "EN"
cpi <- get_data_table(idTable = 50902, shortcut = TRUE, filter = filter,
                      unnest = TRUE, tip = "A", nlast = 5, lang = "EN")
cpi[,c("Nombre", "T3_Periodo", "Anyo", "Valor")]
```

## Use of `unnest`


## Use of `geocode`

## Filter with regular expresions

## periods




